---
title: "Import of TOXSWA files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{toxswa_import}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
```{r setup_hidden, warning=FALSE, results='hide', message=FALSE, echo = FALSE}
options(rmarkdown.html_vignette.check_title = FALSE)

```

```{r setup, warning=FALSE, results='hide', message=FALSE}
library(deeptox)
library(dplyr)
```
This is a primer explaining how to use the function of the deeptox package to load output files from TOXSWA ('.out'-files) and create a simplified timeseries that can be be loaded into DeEP.

Set path to one or more out-files:
```{r set_path1, echo=FALSE}
fpath <- system.file("extdata",package="deeptox") %>%
  list.files("\\d\\.out", full.names = T)
```
```{r set_path2, echo=TRUE, eval=FALSE}
fpath <- c("1.out","2.out","3.out")
```

Read TOXSWA profiles with `readToxswaExpProfiles()`
```{r import_toxswa}
profiles <- readToxswaExpProfiles(fpath)
```
The returned object is a list with one element for each out-file loaded. The names are the filenames without extensions.
```{r show_profile_names}
names(profiles)
```
Each of the list elements is a two-column data.frame with the time in the first column and the external concentration in the second column.
```{r show_profile_ex}
head(profiles[[1]])
```

The profiles can be exported with `write.table()` for later imported into DeEP
```{r write_toxswa, eval = FALSE}
lapply(names(profiles), function(x){
  write.table(profiles[[x]], file = paste0(x,".txt"), row.names = FALSE, col.names = FALSE, sep = "\t")
})
```

Plotting of the profiles is possible with `plotExpProfiles()`
```{r plot_profiles, message=FALSE, warning=FALSE, results='hide'}
lapply(names(profiles), function(x){
  plotExpProfiles(data=profiles[[x]], x="V1", y="V2", title=x)
})
```