---
title: ""
author: ""
date: ""
output: 
  officedown::rdocx_document
  word_document
  html_document
params:
  expProfiles: NA
  parameters: NA
  metaData: NA
  profileResults: NA
  summaryResults: NA
  plotResults: NA
  simulationSettings: NA
  modelParameters: NA
---
```{r importPackagesEtc, echo=FALSE, message=FALSE, warning=FALSE}
options(scipen = 999) # non-scientific number notation

library(dplyr)
library(flextable)
library(xfun)
library(officer)
library(officedown)
library(deeptox)



tabNum <- officer::run_autonum(seq_id = "Table",
                                pre_label = "Table\u00A0",
                                post_label = ": ")

```

```{r prepImportedData, echo=FALSE, message=FALSE}
for( i in names(params) )
  assign(i, params[[i]])
```

```{r settingConst, echo=FALSE, message=FALSE, results='hide'}

paraDescTable <- read.table(paste0(system.file(package="deeptox"),"/app/www/paraDesc.csv"), sep=";", header=T, quote="\"", check.names=FALSE)




#n_profiles = length(vector)
n_profiles <- length(summaryResults[,"profileNames"])
n_profiles
#n_passes = sum(vector)
n_passes <- sum(summaryResults[,"pass_fail_results"]=="Pass")
n_passes
#n_failures = n_profiles – n_passes
n_failures <- n_profiles - n_passes
n_failures

whichFailures <- summaryResults[,"profileNames"][which(summaryResults[,"pass_fail_results"] == "Fail")]
whichFailures
```


:::{custom-style="Title"}
Report DEB-TKTD modelling
:::
:::{custom-style="Date"}
Report generated with deeptox v`r packageVersion("deeptox")` on `r date()`.
:::


# Introduction
DeEP (DEB-TKTD EPx Predictor; Wittwer et al. 2023) was used to predict the effects of `r metaData[["Compound"]]` on *`r metaData[["Species"]]`*. Using the provided parameter set and exposure profile`r pluralS(n_profiles)`, the EP~`r simulationSettings[["ECpct"]]`~ multiplier was predicted with DEB-TKTD modelling (namely the DEBtox 2019 DEB-TKTD model; Jager 2020) to a series of ‘virtual toxicity tests’ (VTTs). This is the factor by which the exposure profiles would need to be multiplied by to cause a `r simulationSettings[["ECpct"]]`% reduction in growth, reproduction, or survival. 

# Overall results

The risk assessment criterion was`r ifelse(n_profiles==1 & n_failures==n_profiles," not","")` met for `r ifelse(n_profiles==1,"", ifelse(n_passes==n_profiles, "all of", ifelse(n_failures==n_profiles, "none of", "some of")))` the exposure profile`r pluralS(n_profiles)` provided.
`r ifelse(n_profiles==1,"In this case", ifelse(n_passes==n_profiles, "In all cases", ifelse(n_failures==n_profiles, "In none of the cases", paste0("In only ",n2w(n_passes), " of ", n2w(n_profiles), " cases"))))` the EP~`r simulationSettings[["ECpct"]]`~ multiplier `r ifelse(n_profiles==1 & n_failures==n_profiles ,"was below","exceeded")` the critical value of `r simulationSettings[["passFail"]]`.
Therefore, `r ifelse(n_passes==n_profiles, paste0("a ",simulationSettings[["ECpct"]],"% reduction in growth, survival, or reproduction would not be expected unless the exposure profile",pluralS(n_profiles)," ",ifelse(n_profiles==1,"was", "were")," multiplied by a factor of >",simulationSettings[["passFail"]],"."), paste0("based on the provided parameters and exposure profile",pluralS(n_profiles),", [compound] may pose an unacceptable risk to [species]."))` The results are summarised in Table \@ref(tab:summaryTable).


# Results table
Table \@ref(tab:summaryTable) shows the results generated for all profiles provided.
```{r summaryTable, echo=FALSE, message=FALSE, results='asis', tab.id="summaryTable"}

# enlarge the critEndpoint column if there are no values, otherwise the column will be very small
if(all(is.na(summaryResults[,"critEndpoint"])))
  summaryResults[,"critEndpoint"] <- "            "

w <- flextable::flextable(summaryResults) %>% 
  dim_pretty(., part="body") %>% 
  .[["widths"]]

w_max <- 6.799 # max width of the table in inches
w_res <- w/sum(w)*w_max

flextable::flextable(summaryResults) %>%
  flextable::width(width = w_res) %>% 
  fontsize(size=8, part="all") %>%
  colformat_num( big.mark="") %>%
  flextable::set_header_labels(values = list(
    profileNames = "Profile names",
    pass_fail_results = "Pass/ Fail",
    critEndpoint = "Critical endpoint",
    total_VTTs = "Total no. of VTTs", 
    No._VTTs_thinned = "No. of VTTs thinned",
    No._VTTs_tested = "No. of VTTs tested")
    ) %>% 
  set_caption(caption="Summary table of all provided profiles indicating passing the critical value for the ‘virtual toxicity tests’ (VTTs).", style="Table caption", autonum = tabNum) %>% 
  flextable::flextable_to_rmd()
```

# Results for individual exposure profiles

```{r indExpProfiles, echo=FALSE, message=FALSE, results='asis', warning=FALSE}
out <- individualExpProfile(summaryResults, simulationSettings, plotResults, profileResults, expProfiles, time_unit = metaData[["Time"]])

```


# Parameters and Setting
Table \@ref(tab:parameterTable) and \@ref(tab:simSettingsTable) contain the parameter values and settings used to make model predictions.
```{r prepParametersTable, echo=FALSE, message=FALSE, results='hide'}

mp <- makeParSettingTable(modelParameters, paraDescTable)

mp.ft <- mp %>% 
  flextable() %>%
  flextable::width(j=1:(ncol(mp)-1), width=4/2.54) %>%
  flextable::width(j=ncol(mp), width=9/2.54) %>%
  colformat_double( big.mark="", digits=3) %>%
  fontsize(size=10, part="all") %>%
  align(i = NULL, j = NULL, align = "left", part = "all") %>% 
  set_caption(caption="Model parameter table", style="Table caption", autonum = tabNum)
```

```{r printParametersTable, echo=FALSE, message=FALSE, results='asis', tab.id="parameterTable"}
mp.ft %>% 
  flextable_to_rmd()
```
 \ 
 

```{r prepSimSettingsTable, echo=FALSE, message=FALSE, results='hide'}

simSet <- makeParSettingTable(c(simulationSettings, metaData[c("Length", "Time", "Concentration")]), paraDescTable)

simSet.ft <- simSet %>% 
  flextable() %>%
  flextable::width(j=1:(ncol(mp)-1), width=4/2.54) %>%
  flextable::width(j=ncol(mp), width=9/2.54) %>%
  fontsize(size=10, part="all") %>%
  align(i = NULL, j = NULL, align = "left", part = "all") %>% 
  colformat_double( big.mark="", digits=3) %>% 
  set_caption(caption="Simulation settings table", style="Table caption", autonum = tabNum)
```

```{r printSimSettingsTable, echo=FALSE, message=FALSE, results='asis', tab.id="simSettingsTable"}
simSet.ft %>% 
  flextable_to_rmd()
```

# References
- Jager, T. (2020). Revisiting simplified DEBtox models for analysing ecotoxicity data. Ecol. Model. 416, 108904. https://doi.org/10.1016/j.ecolmodel.2019.108904
- Wittwer T, Jakoby O, Martin T, Sherborne N, Ashauer R (2023). deeptox: A User-Friendly R-Shiny Application To Make DEB-TKTD Projections Of Sublethal Effects Of Chemical Exposure. R package version `r packageVersion("deeptox")`.


